On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
missing parentheses

\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
\end{align}
%
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$

@@

% WITHOUT J SUBSCRIPT
We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors. By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
\begin{align}\label{stuff}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
\end{align}
%\begin{align}\label{stuff}
%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
%\end{align}
where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.

>>>>

\textbf{Dictionary Recovery:} Fix $\varepsilon < L_{2}(\mathbf{A}) / C_1$.\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} If an $n \times \overline m$ matrix $\mathbf{B}$ has, for every $i \in [N]$, an associated $k$-sparse $\mathbf{\overline x}_i$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$}, then $\overline m \geq m$, and provided that $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- (\mathbf{BPD})_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
\end{align}
%
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$

@@

% WITHOUT J SUBSCRIPT
We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}(\mathbf{A}) / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors. By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
\begin{align}\label{stuff}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
\end{align}
%\begin{align}\label{stuff}
%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
%\end{align}
where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.
